---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include=FALSE}
library(tidyverse)
theme_set(theme_light())
```


# Hi, I'm Devin 

<!-- badges: start -->
<!-- badges: end -->

I'm a Data Scientist with experience working in academic, private, and non-profit research. I work mostly in R but am comfortable with Python and enjoy working in SQL. I'm currently pursuing a PhD in Experimental Psychology, conducting experiments and learning how to leverage existing data to understand human as well as organizational behavior.


I like writing code
```{r}
#Simulation for power analysis

#Compute SD for medium effect (Cohen's D of .5)
solve(0.5, 1)

#Generate number of simulations
n_sims <- 100

p_vals <- c()

for(i in 1:n_sims){
  control_group <- rnorm(60, 0, 2)
  experimental_group <- rnorm(60, 1, 2)
  p_vals[i] <- t.test(control_group, experimental_group)$p.value
}

statistical_power <- mean(p_vals < .05)
statistical_power
```



and making plots


```{r,echo=FALSE}
set.seed(2022)
control_group <- rnorm(60, 0, 2)
experimental_group <- rnorm(60, 1, 2)

sim_data <- as.data.frame(control_group)
sim_data$experimental_group <- experimental_group

sim_data |>
  pivot_longer(names_to = "group",
               values_to = "values",
               cols = c(control_group, experimental_group)) |>
  group_by(group) |>
  summarise(mean_response = mean(values),
            sd = sd(values),
            n = n(),
            sem = sd / sqrt(n)) |>
  ggplot(aes(group, mean_response, fill = group)) +
  geom_col(width = .6) +
  geom_errorbar(mapping = aes(ymin = mean_response - sem,
                              ymax = mean_response + sem),
                width = .4) +
  theme(legend.position="none")
```


```{r,include=FALSE}

report::report(t.test(experimental_group, control_group))
```
